Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-10-20 Paper.Rmd
editting...continued

* Next, we measured 3 types of correlations (Spearman, Kendall, Pearson) and different types of non-parametric tail-dependence difference (see \nameref{NPA}) for both bivariate noise copula and resultant population copula (following model \ref{eq.AR1}) for $50$ simulations. Then we plotted mean of each measured quantity with standard error against Kendall's Tau of the noise copula family. Fig. \ref{fig_Cause4copula_C_kend} compares the statistics from population copula and the copula made of noises drawn from lower tail dependent Clayton family. It is possible to measure the statistics with variation of Spearman's Rho for any other noise copula family (e.g. see Fig. \ref{SM-fig_Cause4copula_SC_spear}). We also carried out a paired t-test to compute the p-values of each statistic for noise and population data and found that like our first approach (model selection method), here also the nature of tail dependence in noise and populations remained similar but they were not exactly the same except in Pearson correlation coefficient which ensured the Moran effect on the population data caused by environmental noise. (For code see [`Plotter_Cause4copula_stat`](https://github.com/sghosh89/BIVAN/blob/master/Cause4copula.R) function).

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Corl-Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Pl-Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_D2u-D2l_vs_Kendall's Tau.pdf}
\caption[Comparing correlations and non-parametric statistic between noise-copula (\textbf{Clayton}) and population copula for different \textbf{Kendall's Tau}]{Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 3 non-parametric stats ($\cor_l - \cor_u$, $\Ps_l - \Ps_u$ and $\Dsq_u - \Dsq_l$) of environmental noise generated from lower tail dependent \textbf{Clayton} copula and of the affected populations for 9 equidistant \textbf{Kendall's Tau} values in a range (0.1 to 0.9) (Initially $5000$ points are generated but we kept last $500$ points for both noise and population data for comparison). p-values $< 0.05$ (below horizontal purple line) indicates significantly similar estimate between noise and population copulae. \label{fig_Cause4copula_C_kend}}
\end{center}
\end{figure}

>>>>

* Next, we measured 3 types of correlations (Spearman, Kendall, Pearson) and different types of non-parametric tail-dependence statistics (see \nameref{NPA}) for both bivariate noise copula and resultant population copula (following model \ref{eq.AR1}) for $50$ simulations. Then we plotted mean of each measured quantity with standard error against Kendall's Tau of the noise copula family. Fig. \ref{SM-fig_Cause4copula_C_kend} compares the statistics from population copula and the copula made of noises drawn from lower tail dependent Clayton family. It is possible to measure the statistics with variation of Spearman's Rho for any other noise copula family (e.g. see Fig. \ref{SM-fig_Cause4copula_SC_spear}). We also carried out a paired t-test to compute the p-values of each statistic for noise and population data and found that like our first approach (model selection method), here also the nature of tail dependence in noise and populations remained similar but they were not exactly the same except in Pearson correlation coefficient which ensured the Moran effect on the population data caused by environmental noise. (For code see [`Plotter_Cause4copula_stat`](https://github.com/sghosh89/BIVAN/blob/master/Cause4copula.R) function). Linear regression between tail statistics from noise and population copula (Fig. \ref{fig_Cause4copula_scatter_C_kend}) confirmed that the asymmetric tail dependence in noise copula caused similar tail dependence in population copula.

\begin{figure}[!h]
\begin{center}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_scatter_D2umD2l_Kendall's Tau.pdf}
\caption{Linear regression between 3 non-parametric stats ($\cor_l - \cor_u$, $\Ps_l - \Ps_u$ and $\Dsq_u - \Dsq_l$) of environmental noise generated from lower tail dependent \textbf{Clayton} copula and of the affected populations for 9 equidistant \textbf{Kendall's Tau} values in a range (0.1 to 0.9 as shown in Fig. \ref{SM-fig_Cause4copula_C_kend}) showed significant pearson correlation, and henceforth confirmed asymmetric tail dependence in noise copula caused similar tail dependence in population copula.\label{fig_Cause4copula_scatter_C_kend}}
\end{center}
\end{figure}

### 2018-10-20 SupportingInformation.Rmd
editting...continued

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_Spearman_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_Kendall_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_Pearson_vs_Spearman's Rho.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_Corl-Coru_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_Pl-Pu_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_D2u-D2l_vs_Spearman's Rho.pdf}
\caption[Comparing correlations and non-parametric statistic between noise-copula (\textbf{Clayton}) and population copula for different \textbf{Spearman's Rho}]{Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 3 non-parametric stats ($\cor_l - \cor_u$, $\Ps_l - \Ps_u$ and $\Dsq_u - \Dsq_l$) of environmental noise generated from upper-tail dependent \textbf{Survival Clayton} copula and of the affected populations for 9 equidistant \textbf{Kendall's Tau} values in a range (0.1 to 0.9) (Initially $5000$ points are generated but we kept last $500$ points for both noise and population data for comparison). p-values $< 0.05$ (below horizontal purple line) indicates significantly similar estimate between noise and population copulae. \label{fig_Cause4copula_SC_spear}}
\end{center}
\end{figure}

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_D2u-D2l_vs_Kendall's Tau.pdf}
\caption[Comparing correlations and non-parametric statistic between noise-copula (\textbf{Clayton}) and population copula for different \textbf{Kendall's Tau}]{Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from lower tail dependent \textbf{Clayton} copula and of the affected populations for 9 equidistant \textbf{Kendall's Tau} values in a range (0.1 to 0.9) (Initially $5000$ points are generated but we kept last $500$ points for both noise and population data for comparison). p-values from paired t-test if $> 0.05$ (above horizontal purple line) indicates exactly same estimate between noise and population copulae. \label{fig_Cause4copula_C_kend}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Spearman_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Kendall_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Pearson_vs_Spearman's Rho.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Corl_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Coru_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_Corl-Coru_vs_Spearman's Rho.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_Pl_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_Pu_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_Pl-Pu_vs_Spearman's Rho.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_D2u_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_D2l_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_D2u-D2l_vs_Spearman's Rho.pdf}
\caption[Comparing correlations and non-parametric statistic between upper tail dependent noise-copula (\textbf{Survival Clayton}) and population copula for different \textbf{Spearman's Rho}]{Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from upper tail dependent \textbf{Survival Clayton} copula and of the affected populations for 9 equidistant \textbf{Spearman's Rho} values in a range (0.1 to 0.9) (Initially $5000$ points are generated but we kept last $500$ points for both noise and population data for comparison). p-values from paired t-test if $> 0.05$ (above horizontal purple line) indicates exactly same estimate between noise and population copulae. \label{fig_Cause4copula_SC_spear}}
\end{center}
\end{figure}
